An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-29 main.tex
Minor reorganisation of files.

\usepackage[backend=biber, firstinits=false, backref=false, url=true,
            isbn=true, style=numeric]{biblatex}
\addbibresource{bibliography.bib}

@@

\begin{figure}[!hbtp]
    \centering
    \input{../img/moran_process.tex}
    \caption{A diagrammatic representation of a Moran process}
    \label{fig:moran_process}
\end{figure}

@@

Appendix~\ref{app:list_of_players} shows all the players in question. More
information about each player can be obtained in the documentation for
\cite{axelrodproject}. There are \input{../tbl/num_stochastic.tex}stochastic and
\input{../tbl/num_deterministic.tex}deterministic strategies. Their memory
depth is shown in Table~\ref{tbl:memory_depth_count}.

\begin{table}[!hbtp]
    \centering
        \input{../tbl/memory_depth_count.tex}
        \caption{Memory depth}
        \label{tbl:memory_depth_count}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{../img/number_of_match_outcomes.pdf}
        \caption{All matches}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{../img/number_of_stochastic_match_outcomes.pdf}
        \caption{Stochastic matches}
    \end{subfigure}%
    \caption{The distribution of the number of unique outcomes used as the
    cached results}
    \label{fig:number_of_stochastic_match_outcomes}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{../tbl/number_of_match_outcomes.tex}
        \caption{All matches}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{../tbl/number_of_stochastic_match_outcomes.tex}
        \caption{Stochastic matches}
    \end{subfigure}%
    \caption{Summary statistics for the number of different match outcomes used
    as the cached results}
    \label{tbl:number_of_stochastic_match_outcomes}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_v_Tit_For_Tat.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Random_v_Cooperator.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Random_v_Defector.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Random_v_Tit_For_Tat.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator.pdf}
        \caption{All C or all D and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector.pdf}
        \caption{All C or all D and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random.pdf}
        \caption{Calculator and Random}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies}
    \label{fig:comparison_stochastic}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}[t]{.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/fixation_heatmap_2_invade.pdf}
        % TODO Remove this: I don't feel it is effective.
        \caption{The pairwise fixation probabilities for \(N=2\)}
        \label{fig:fixation_heatmap_2}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.6\textwidth}
        \centering
        \includegraphics[height=.8\textheight]{../img/boxplot_2_invade.pdf}
        \caption{The median fixation probabilities for \(N=2\)}
        \label{fig:boxplot_2}
    \end{subfigure}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \input{../tbl/summary_top_2_invade.tex}
    \caption{Summary of top five strategies for \(N=2\)}
    \label{tbl:summary_top_2}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \input{../img/invasion_resistance.tex}
    \caption{A single individual will successfully invade the population with
    probability \(x_1\). The group of Individuals will successfully resist with
    probability \(x_{N-1}\)}
    \label{fig:invasion_resistance}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
        \caption{\(N=12\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_12_invade.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_resist.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_resist.pdf}
        \caption{\(N=12\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_resist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_12_resist.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invade.pdf}
    \caption{invade}
    \label{fig:ranks_v_size_invade}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resist.pdf}
    \caption{resist}
    \label{fig:ranks_v_size_resist}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_coexist.pdf}
    \caption{Coexistance}
    \label{fig:ranks_v_size_coexist}
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_invade.tex"}
        \caption{Correlation coefficients for ranks for invasion}
        \label{tbl:correlation_coeficients_invade}
    \end{subfigure}%

    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_resist.tex"}
        \caption{Correlation coefficients for ranks for resistance}
        \label{tbl:correlation_coeficients_resist}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_coexist.tex"}
        \caption{Correlation coefficients for ranks for coexistance}
        \label{tbl:correlation_coeficients_coexist}
    \end{subfigure}
    \caption{Correlation coefficients of rankings by population size}
\end{table}

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_invade.pdf}
		\caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size}
    \label{fig:correlation_coefficients}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.6\textwidth]{../img/fixation_v_fitness_illustration.pdf}
    \caption{\(x_i(r)\)}
    \label{fig:fixation_v_fitness_illustration}
\end{figure}

@@

\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime}
    \frac{dx_i}{dr} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime.tex}
\end{equation}

\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime2}
    \frac{d^2x_i}{dr^2} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime2.tex}
\end{equation}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_fitness.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_fitness.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_fitness.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat_fitness.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator_fitness.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat_fitness.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

>>>>

\usepackage[backend=biber, firstinits=false, backref=false, url=true,
            isbn=true, style=numeric]{biblatex}
\addbibresource{./tex/bibliography.bib}

@@

\begin{figure}[!hbtp]
    \centering
    \input{./tex/moran_process.tex}
    \caption{A diagrammatic representation of a Moran process}
    \label{fig:moran_process}
\end{figure}

@@

Appendix~\ref{app:list_of_players} shows all the players in question. More
information about each player can be obtained in the documentation for
\cite{axelrodproject}. There are \input{./tex/num_stochastic.tex}stochastic and
\input{./tex/num_deterministic.tex}deterministic strategies. Their memory
depth is shown in Table~\ref{tbl:memory_depth_count}.

\begin{table}[!hbtp]
    \centering
        \input{./tex/memory_depth_count.tex}
        \caption{Memory depth}
        \label{tbl:memory_depth_count}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{./img/number_of_match_outcomes.pdf}
        \caption{All matches}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{./img/number_of_stochastic_match_outcomes.pdf}
        \caption{Stochastic matches}
    \end{subfigure}%
    \caption{The distribution of the number of unique outcomes used as the
    cached results}
    \label{fig:number_of_stochastic_match_outcomes}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/number_of_match_outcomes.tex}
        \caption{All matches}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{./tex/number_of_stochastic_match_outcomes.tex}
        \caption{Stochastic matches}
    \end{subfigure}%
    \caption{Summary statistics for the number of different match outcomes used
    as the cached results}
    \label{tbl:number_of_stochastic_match_outcomes}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Tit_For_Tat.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_Tit_For_Tat.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Tit_For_Tat.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Win-Stay_Lose-Shift_v_Tit_For_Tat.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Win-Stay_Lose-Shift.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Win-Stay_Lose-Shift.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Tit_For_Tat.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Cooperator.pdf}
        \caption{All C or all D and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Defector.pdf}
        \caption{All C or all D and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Random.pdf}
        \caption{Calculator and Random}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Tit_For_Tat.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies}
    \label{fig:comparison_stochastic}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}[t]{.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/fixation_heatmap_2_invade.pdf}
        % TODO Remove this: I don't feel it is effective.
        \caption{The pairwise fixation probabilities for \(N=2\)}
        \label{fig:fixation_heatmap_2}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.6\textwidth}
        \centering
        \includegraphics[height=.8\textheight]{./img/boxplot_2_invade.pdf}
        \caption{The median fixation probabilities for \(N=2\)}
        \label{fig:boxplot_2}
    \end{subfigure}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \input{./tex/summary_top_2_invade.tex}
    \caption{Summary of top five strategies for \(N=2\)}
    \label{tbl:summary_top_2}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \input{./tex/invasion_resistance.tex}
    \caption{A single individual will successfully invade the population with
    probability \(x_1\). The group of Individuals will successfully resist with
    probability \(x_{N-1}\)}
    \label{fig:invasion_resistance}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_12_invade.pdf}
        \caption{\(N=12\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/boxplot_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/boxplot_12_invade.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_12_invade.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_3_resist.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_12_resist.pdf}
        \caption{\(N=12\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/boxplot_3_resist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/boxplot_12_resist.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_12_resist.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_invade.pdf}
    \caption{invade}
    \label{fig:ranks_v_size_invade}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_resist.pdf}
    \caption{resist}
    \label{fig:ranks_v_size_resist}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_coexist.pdf}
    \caption{Coexistance}
    \label{fig:ranks_v_size_coexist}
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \input{"./tex/correlation_coeficients_invade.tex"}
        \caption{Correlation coefficients for ranks for invasion}
        \label{tbl:correlation_coeficients_invade}
    \end{subfigure}%

    \begin{subfigure}{\textwidth}
        \centering
        \input{"./tex/correlation_coeficients_resist.tex"}
        \caption{Correlation coefficients for ranks for resistance}
        \label{tbl:correlation_coeficients_resist}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \input{"./tex/correlation_coeficients_coexist.tex"}
        \caption{Correlation coefficients for ranks for coexistance}
        \label{tbl:correlation_coeficients_coexist}
    \end{subfigure}
    \caption{Correlation coefficients of rankings by population size}
\end{table}

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{./img/correlation_heatmap_invade.pdf}
		\caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{./img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{./img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size}
    \label{fig:correlation_coefficients}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.6\textwidth]{./img/fixation_v_fitness_illustration.pdf}
    \caption{\(x_i(r)\)}
    \label{fig:fixation_v_fitness_illustration}
\end{figure}

@@

\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime}
    \frac{dx_i}{dr} = \input{./tex/fixation_probability_with_constant_relative_fitness_prime.tex}
\end{equation}

\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime2}
    \frac{d^2x_i}{dr^2} = \input{./tex/fixation_probability_with_constant_relative_fitness_prime2.tex}
\end{equation}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator_fitness.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector_fitness.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Tit_For_Tat_fitness.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_Tit_For_Tat_fitness.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator_fitness.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Tit_For_Tat_fitness.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Win-Stay_Lose-Shift_v_Tit_For_Tat_fitness.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Win-Stay_Lose-Shift_fitness.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Win-Stay_Lose-Shift_fitness.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Estimated relative fitness
             for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator_fitness.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector_fitness.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Tit_For_Tat_fitness.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%
